An Investigation of Confusing Code Patterns in JavaScript

### 2022-10-31 3_Method.tex
Fernando tackled the reviewer comments assigned to him by Rodrigo.

% The design of the repeated measures study considers two treatments: the presence or absence of atom candidates within the programs.
To identify atom candidates, we start out by selecting every atom candidate from Gopstein's study that can also happen in JavaScript. That excludes atoms related to pointers and preprocessor directives. Furthermore, we conduct an informal search of programming forums, solutions to Code Golf~\footnote{https://codegolf.stackexchange.com/} problems, code style guidelines, and expert knowledge to identify new atom candidates. Overall, the repeated measures study analyzes 24 atoms, 15 from the original study and 9 that are new. Some of these atoms are also analyzed in the Latin square study (Section~\ref{sec:meth:survey}). Table~\ref{tab:atomsBoth} presents the atom candidates that both studies investigate and Table~\ref{tab:atomsRepeated} presents the ones that only the repeated measures study analyzes.

>>>>

% The design of the repeated measures study considers two treatments: the presence or absence of atom candidates within the programs.
To identify atom candidates, we start out by selecting every atom candidate from Gopstein's study that can also happen in JavaScript. That excludes atoms related to pointers and preprocessor directives. Furthermore, we conduct an informal search of \revised{JavaScript questions on StackOverflow about constructs that are not typical of other languages, such as array and object spread, solutions to Code Golf~\footnote{https://codegolf.stackexchange.com/} problems, and code style guides\footnote{AirBNB JavaScript Style Guide: https://github.com/airbnb/javascript}\footnote{Google JavaScript Style Guide: https://google.github.io/styleguide/jsguide.html} to identify new atom candidates. We leverage previous work~\cite{castor2018} on the identification of atom candidates to guide us in this informal search.} Overall, the repeated measures study analyzes 24 atoms, 15 from the original study and 9 that are new. Some of these atoms are also analyzed in the Latin square study (Section~\ref{sec:meth:survey}). Table~\ref{tab:atomsBoth} presents the atom candidates that both studies investigate and Table~\ref{tab:atomsRepeated} presents the ones that only the repeated measures study analyzes.
